---
title: "Examples for 'A framework for styding cyclones'"
author: "JAH"
date: "5/13/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Here, we use data for three examples that illustrate the implementation of the reserach framework. 

1. We compare response of stream biogeochemistry (NO3 and K) from two tropical headwater streams that differ in cyclone frequency.  The watershed in Fushan experiences a damaging cyclone (cat. 4 or greater) very frequenly (approximately annualy), and the watershed in Luquillo experiences them occasionally (approximately decadaly)

2. We compare the GPP responses of three coastal marshes (Texas, New Jersey and Lousiana), where cyclone timing was a major infleuncing factor.

3. We look at fish abundance data from four estuaries in Texas that expereinced differing storm strenght (rainfall total and windspeeds) during Hurricane Harvey in 2017. 

```{r cars}
### read in the data
library(readr)

########## LUQUILLO
LUQ_K <- read_csv("C:/Users/hogie/Dropbox (Personal)/LUQ LITTERFALL for Hurricane Workshop 4.2019/CONCEPTUAL PAPER/Stream Nutrents_CHIUandMcDOWELL/LUQ_QSmonthlyK.csv",
col_types = cols(Month_Yr = col_date(format = "%b-%y")))

LUQ_NO3 <- read_csv("C:/Users/hogie/Dropbox (Personal)/LUQ LITTERFALL for Hurricane Workshop 4.2019/CONCEPTUAL PAPER/Stream Nutrents_CHIUandMcDOWELL/LUQ_QSmonthlyNO3.csv",
col_types = cols(Month_Yr = col_date(format = "%b-%y")))

########## FUSHAN
FUS_K <- read_csv("C:/Users/hogie/Dropbox (Personal)/LUQ LITTERFALL for Hurricane Workshop 4.2019/CONCEPTUAL PAPER/Stream Nutrents_CHIUandMcDOWELL/FUSHAN_WS4_monthlyK.csv", col_types = cols(date = col_date(format = "%m/%d/%Y")))

FUS_NO3 <- read_csv("C:/Users/hogie/Dropbox (Personal)/LUQ LITTERFALL for Hurricane Workshop 4.2019/CONCEPTUAL PAPER/Stream Nutrents_CHIUandMcDOWELL/FUSHAN_WS4_monthlyNO3.csv", col_types = cols(date = col_date(format = "%m/%d/%Y")))
```

# Stream Nitrate
## LUQ
### NO3 - N
```{r pressure, echo=FALSE}
library(ggplot2)

g_LUQ_NO3 <- ggplot(aes(Month_Yr, `NO3 (ugN/L)`), data = LUQ_NO3) + geom_line() + geom_point(size = 0.5) +
                 scale_x_date(date_labels = "%b-%Y") + xlab("") + 
                 ylab(expression("stream nitrate"*"  ("* mu*"g N L"^-1* ")")) + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +  
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico")




g_LUQ_NO3_2 <- ggplot(aes(Month_Yr, `NO3 (ugN/L)`), data = LUQ_NO3[LUQ_NO3$Month_Yr< "2005-01-01",]) + geom_line() + geom_point(size = 0.5) +
                 scale_x_date(date_labels = "%b-%Y") + xlab("") + ylab("") +
                theme_classic() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red") +  
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red") # + ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico")


g_LUQ_NO3


g_LUQ_NO3_2

```

### K 
```{r}
g_LUQ_K <- ggplot(aes(Month_Yr, `K (mg/L)`), data = LUQ_K) + geom_line() + geom_point() +     
                 scale_x_date(date_labels = "%b-%Y") + xlab("") + 
                 ylab(expression("stream potassium"*"  (mg K L"^-1* ")")) + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico")

g_LUQ_K
```

## FUSHAN
### NO3 - N
```{r, echo=FALSE}

g_FUS_NO3 <- ggplot(aes(date, `NO3 (ugN/L)`), data = FUS_NO3) + geom_line() + geom_point(size = 0.75) +     
                 scale_x_date(date_labels = " %Y") + xlab("") + 
                 ylab("") + theme_minimal() +
                 geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + 
geom_vline(xintercept = as.Date("07-10-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-08-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-07-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-31-1996", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-15-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-18-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-31-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-02-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-18-2007", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-06-2007", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-12-2008", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-28-2008", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-12-2013", format = "%m-%d-%Y"), col = "red",  linetype="dotted")  + ylim(c(0, 700)) + theme(axis.title.x = element_blank()) #+ ggtitle("Watershed 4, Leinhuachi Experimental Forest, Taiwan")


g_FUS_NO3_2 <- ggplot(aes(date, `NO3 (ugN/L)`), data = FUS_NO3[FUS_NO3$Year < 2005,]) + geom_line() + geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%b-%Y") + xlab("") + 
                 ylab("") + theme_classic() +
                 geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + 
geom_vline(xintercept = as.Date("07-10-1994", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("08-08-1994", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("10-07-1994", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("07-31-1996", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("10-15-1998", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("07-18-2005", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("08-31-2005", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("10-02-2005", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("08-18-2007", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("10-06-2007", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("09-12-2008", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("09-28-2008", format = "%m-%d-%Y"), col = "red")+
geom_vline(xintercept = as.Date("07-12-2013", format = "%m-%d-%Y"), col = "red") + ylim(c(0, 700)) + theme(axis.title.x = element_blank()) #+ ggtitle("Watershed 4, Leinhuachi Experimental Forest, Taiwan")


g_FUS_NO3

g_FUS_NO3_2
```

### K 
```{r}
g_FUS_K <- ggplot(aes(date, `K (mg/L)`), data = FUS_K) + geom_line() + geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%Y") + xlab("") + 
                 ylab(expression("stream potassium"*"  (mg K L"^-1* ")")) + theme_minimal() +
geom_vline(xintercept = as.Date("07-10-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-08-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-07-1994", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-31-1996", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-15-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-18-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-31-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-02-2005", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("08-18-2007", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("10-06-2007", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-12-2008", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-28-2008", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("07-12-2013", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ylim(c(0.0, 0.7)) + theme(axis.title.x = element_blank()) #+ ggtitle("Watershed 4, Leinhuachi Experimental Forest, Taiwan") 

g_FUS_K
```

```{r}
## ALL TOGETHER
### need to subset LUQ data
g_LUQ_NO3_short <- ggplot(aes(Month_Yr, `NO3 (ugN/L)`), data = LUQ_NO3[127:351,]) + geom_line() + 
                 geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%Y") + xlab("") + 
                 ylab("") + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +  
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ylim(c(0, 600)) + theme(axis.title.x = element_blank()) #+ ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico") 


g_LUQ_K_short <- ggplot(aes(Month_Yr, `K (mg/L)`), data = LUQ_K[129:372,]) + geom_line() + 
                 geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%Y") + xlab("") + 
                 ylab("") + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ylim(c(0.0, 0.7)) + theme(axis.title.x = element_blank()) #+ ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico") 
```

```{r}
####
library(ggpubr)

tiff()

double_K <- ggarrange(g_LUQ_K_short, g_FUS_K + ylab(""), nrow = 2, labels = "AUTO")

double_K <- annotate_figure(double_K, left = text_grob(expression("stream potassium"*"  (mg K L"^-1* ")"), rot = 90))

double_K


tiff(filename = "Streams_potassium.tiff", width = 18.5, height = 5.745, units = "cm",res = 600, compression = "lzw")
double_K
dev.off()


```



```{r}
#### ggarrange 
double_NO3 <- ggarrange(g_LUQ_NO3_short, g_FUS_NO3, nrow = 2, labels = "AUTO")

double_NO3 <- annotate_figure(double_NO3, left = text_grob(expression("stream nitrate"*"  ("* mu*"g N L"^-1* ")"), rot = 90))

double_NO3


tiff(filename = "Streams_nitrate.tiff", width = 18.5, height = 5.745, units = "cm",res = 600, compression = "lzw")
double_NO3
dev.off()
```


```{r}
##############################
## After Bill McDowells email: 
### 1) Plot only through 2004 (i.e. to 2015)

## ALL TOGETHER
### need to subset LUQ data
g_LUQ_NO3_short <- ggplot(aes(Month_Yr, `NO3 (ugN/L)`), data = LUQ_NO3[127:351,]) + geom_line() + 
                 geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%Y") + xlab("") + 
                 ylab("") + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +  
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ylim(c(0, 600)) + theme(axis.title.x = element_blank()) #+ ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico") 


g_LUQ_K_short <- ggplot(aes(Month_Yr, `K (mg/L)`), data = LUQ_K[129:372,]) + geom_line() + 
                 geom_point(size = 0.75) +     
                 scale_x_date(date_labels = "%Y") + xlab("") + 
                 ylab("") + theme_minimal() +
geom_vline(xintercept = as.Date("09-18-1989", format = "%m-%d-%Y"), col = "red",  linetype="dotted") +
geom_vline(xintercept = as.Date("09-21-1998", format = "%m-%d-%Y"), col = "red",  linetype="dotted") + ylim(c(0.0, 0.7)) + theme(axis.title.x = element_blank()) #+ ggtitle("Quebrada Sonadora, Luquillo Experimental Forest, Puerto Rico") 
```

```{r}
####
library(ggpubr)

tiff()

double_K <- ggarrange(g_LUQ_K_short, g_FUS_K + ylab(""), nrow = 2, labels = "AUTO")

double_K <- annotate_figure(double_K, left = text_grob(expression("stream potassium"*"  (mg K L"^-1* ")"), rot = 90))

double_K


tiff(filename = "Streams_potassium.tiff", width = 18.5, height = 5.745, units = "cm",res = 600, compression = "lzw")
double_K
dev.off()


```



```{r}
#### ggarrange 
double_NO3 <- ggarrange(g_LUQ_NO3_short, g_FUS_NO3, nrow = 2, labels = "AUTO")

double_NO3 <- annotate_figure(double_NO3, left = text_grob(expression("stream nitrate"*"  ("* mu*"g N L"^-1* ")"), rot = 90))

double_NO3

###################
double_NO3_2 <- ggarrange(g_LUQ_NO3_2, g_FUS_NO3_2, nrow = 2)

double_NO3_2 <- annotate_figure(double_NO3_2, left = text_grob(expression("stream nitrate"*"  ("* mu*"g N L"^-1* ")"), rot = 90))

double_NO3_2



# 
# tiff(filename = "Streams_nitrate.tiff", width = 18.5, height = 5.745, units = "cm",res = 600, compression = "lzw")
# double_NO3
# dev.off()
# 



tiff(filename = "Streams_nitrate_2_10.30.19.tiff", width = 18.5, height = 8.6205, units = "cm",res = 600, compression = "lzw")
double_NO3_2
dev.off()
```

# Marsh GPP
```{r}
library(readxl)
marshGPP <-  read_xlsx(path = "C:/Users/hogie/Dropbox (Personal)/LUQ LITTERFALL for Hurricane Workshop 4.2019/CONCEPTUAL PAPER/Rusty & Chris Data/RustysGPP_LONG.xlsx", col_types = c("text", "date", "numeric", "numeric", "guess", "guess"))

marshGPP$GPP <-  as.numeric(marshGPP$GPP)
marshGPP$Hurricane <-  as.factor(marshGPP$Hurricane)

```

```{r}
library(tidyverse)

std_err <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}

marsh_ordinalGPP <- marshGPP %>% filter(Hurricane == "NA") %>% group_by(Site, `Ordinal Date`) %>% summarise(avgGPP = mean(GPP, na.rm = T), sdGPP = sd(GPP, na.rm = T))
```

```{r}
library(awtools)
library(ggthemes)


gg.RUSTY <- ggplot(aes(x = `Ordinal Date`, y=avgGPP), data = marsh_ordinalGPP) + geom_point(data = marshGPP[!marshGPP$Hurricane == "NA",], aes(x = `Ordinal Date`, y=GPP, color = Hurricane), size = 1) + geom_line(aes(x = `Ordinal Date`,  y=GPP, color = Hurricane), data = marshGPP[!marshGPP$Hurricane == "NA",], size = 0.5) + geom_point(size = 1.5) +  geom_errorbar(aes(ymin=avgGPP-sdGPP, ymax=avgGPP+sdGPP), data = marsh_ordinalGPP)  + facet_wrap(vars(Site)) + scale_x_continuous(breaks = c(1,91,182,274,366), labels=c("Jan","Apr","Jul","Oct", "Jan")) + scale_y_continuous(labels = function(x)x*12, limits = c(0,1)) + theme_minimal()  + theme(axis.title.x=element_blank()) + ylab(expression(paste("GPP (gC m"^-2*" d"^-1*")"))) + scale_color_manual(values = mpalette[1:6], breaks = c("Katrina", "Gustav", "Isaac", "Sandy", "Ike", "year after Ike")) #+ ggtitle("Productivity from Three USA Coastal Marshes ") 
 
gg.RUSTY


gg.RUSTY_NOV <- ggplot(aes(x = `Ordinal Date`, y=avgGPP), data = marsh_ordinalGPP) +    geom_ribbon(aes(ymin=avgGPP-sdGPP, ymax=avgGPP+sdGPP), data = marsh_ordinalGPP, fill = "grey70") + geom_point(data = marshGPP[!marshGPP$Hurricane == "NA",], aes(x = `Ordinal Date`, y=GPP, color = Hurricane), size = 2) + geom_line(aes(x = `Ordinal Date`,  y=GPP, color = Hurricane), data = marshGPP[!marshGPP$Hurricane == "NA",], size = 0.75) + facet_wrap(vars(Site)) + scale_x_continuous(breaks = c(1,91,182,274,366), labels=c("Jan","Apr","Jul","Oct", "Jan")) + scale_y_continuous(labels = function(x)x*12, limits = c(0,1)) + theme_classic()  + theme(axis.title.x=element_blank()) + ylab(expression(paste("GPP (gC m"^-2*" d"^-1*")"))) + scale_color_manual(values = colorblind_pal()(8)[c(1,2,4,5,6,8)], breaks = c("Katrina", "Gustav", "Isaac", "Sandy", "Ike", "year after Ike")) #+ ggtitle("Productivity from Three USA Coastal Marshes ") 
 
gg.RUSTY_NOV 
```

# Fish Abundances
```{r}
library(readr)
bag_seine <- read_csv("CONCEPTUAL PAPER/Rusty & Chris Data/Supplement.2F.BagSeine.csv",
col_types = cols(Date = col_date(format = "%m/%d/%Y")))

delta_catch <- read_csv("CONCEPTUAL PAPER/Rusty & Chris Data/Supplement.2G.HistoricDeltaCatch.csv")


```

```{r}
avg.bag_siene <- bag_seine %>% group_by(Estuary, Month) %>%  summarise(avg = mean(`Total Catch`, na.rm = T), se = std_err(`Total Catch`, na.rm = T))

avg.delta_catch<- delta_catch[delta_catch$Period == "PreHarvey",] %>% group_by(Estuary.Name) %>% summarize(avg = mean(PerChangeAug.Sept), se = std_err(PerChangeAug.Sept, na.rm = T))

avg.bag_siene <- bag_seine %>% group_by(Estuary, Month) %>%  summarise(avg = mean(`Total Catch`, na.rm = T), se = std_err(`Total Catch`, na.rm = T))
                                                            avg.bag_siene$wind_speed <- c(rep(140, 6),  rep(100,6), rep(120,6), rep(60,6))
```

```{r}

gg.ChrisPatrick1 <- ggplot(aes(x = `Month`, y=avg, color = wind_speed, shape = Estuary), data = avg.bag_siene) + geom_point(position=position_dodge(width=0.3)) + geom_line(position=position_dodge(width=0.3)) + geom_errorbar(aes(ymin=avg-se, ymax=avg+se), position=position_dodge(width=0.3), width=0.5)  + theme_classic()  + theme(axis.title.x=element_blank()) + ylab("Fish Abundance (Siene CPUE)") + scale_color_gradient(low = "blue", high = "red", guide = "none") + scale_x_continuous(breaks = c(7:12), labels=c("Jul","Aug","Sep","Oct", "Nov", "Dec")) + theme(legend.position = c(0.4, 0.85), legend.title = element_blank()) #+ ggtitle("Changes in Fish Abundance after Hurrican Harvey in Texas, 2017") 
 
gg.ChrisPatrick1
```

```{r}
avg.bag_siene2 <- bag_seine %>% group_by(Estuary, Date) %>%  summarise(avg = mean(`Total Catch`, na.rm = T), se = std_err(`Total Catch`, na.rm = T))
```

```{r}
xxx <- cbind(delta_catch[delta_catch$Period == "Harvey",c(3,4)], rep(NA, 4))

colnames(xxx) <- c("Estuary.Name", "avg", "se")

Estuary_frame <-  rbind(rbind(cbind(xxx, period = rep("Windspeed (MPH)", 4))), rbind(cbind(avg.delta_catch, period = rep("2010-16", 4))))

Estuary_frame$Estuary.Name <- factor(Estuary_frame$Estuary.Name, levels = c("San Antonio Bay", "Aransas Bay", "Corpus Christi Bay", "Upper Laguna Madre"))

```

```{r}
gg.ChrisPatrick2 <- ggplot(aes(x = Estuary.Name, y = avg, fill = period), data = Estuary_frame) + geom_bar(stat = "identity", position = "dodge") + geom_errorbar(aes(ymin=avg-se, ymax=avg+se), position= "dodge", color = "#999999")  + theme_classic()  + theme(axis.title.x=element_blank()) + ylab("Propotion change CPUE Aug to Sep") + scale_fill_manual(values = c("#B22222", "#999999")) + theme(legend.position = c(0.8, 0.19), legend.title = element_blank()) + scale_x_discrete(labels = c("San Antonio Bay" = "San\nAntionio", "Aransas Bay" = "Aransas", "Corpus Christi Bay" = "Corpus\nChristi", "Upper Laguna Madre" = "Upper\nLaguna\nMadre")) + ylim(c(-1, 0.5)) #+ ggtitle("Changes in Fish Abundance after Hurrican Harvey in Texas, 2017")  
 
gg.ChrisPatrick2
```

#####

```{r}
#tiff(filename = "FFFFF.tiff", width = 19.05, height = 19.05, units = "cm", res = 600, compression = "lzw")
ggarrange(gg.RUSTY_NOV, double_NO3_2, ggarrange(gg.ChrisPatrick1, gg.ChrisPatrick2, ncol =2), nrow = 3)
#dev.off()
```
